 

### 2020-11-15 doc/manuscript/MEE_manuscript.Rmd
update sites table
corrected climate, Harvard Forest references

**Table 1 | Sites included in this analysis**. Here and throughout, sites are ordered by descending mean annual temperature. Additional site information is provided in Table S1, and species and their sample sizes are detailed in Tables S2-S3. *Climate will be filled in based on CRU data.*
![ ](tables_figures/sites_table.png)
```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @alfaro-sanchez_growth_2017; @helcoski_growing_2019; @gonzalez-akre_scbi-forestgeoscbi-forestgeo-data_2020-1; @aus_de_ar_tree_2018; @bumann_assessing_2019; @samonil_individual-based_2013; @kaspar_species-specific_nodate
---

>>>>

**Table 1 | Sites included in this analysis**. Here and throughout, sites are ordered by descending mean annual temperature. Additional site information is provided in Table S1, and species and their sample sizes are detailed in Tables S2-S3. 
![ ](tables_figures/sites_table.png)
```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @alfaro-sanchez_growth_2017; @helcoski_growing_2019 @gonzalez-akre_scbi-forestgeoscbi-forestgeo-data_2020-1; @aus_de_ar_tree_2018; @bumann_assessing_2019; @samonil_individual-based_2013; @kaspar_species-specific_nodate; @alexander_potential_2019; @finzi_carbon_2020
---

### 2020-11-15 doc/manuscript/tables_figures/sites_table.Rmd
update sites table
corrected climate, Harvard Forest references

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
sites <- read.csv("sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
sites_table <- subset(sites, select = -c(MAT) )
kable(sites_table, format = "latex", booktabs = TRUE,  escape = F)%>%
  column_spec(1, width = "1cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "3cm") %>%
  #column_spec(6, width = ".5cm") %>%
  column_spec(7, width = "1.4cm") %>%
  column_spec(8, width = "1cm") %>%
  #column_spec(9, width = "2cm") %>%
  column_spec(10, width = "3cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
*don't trust this climate data

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
sites <- read.csv("sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
sites_table <- subset(sites, select = -c(MAT) ) #drop MAT column
kable(sites_table, format = "latex", booktabs = TRUE,  escape = F)%>%
  add_header_above(c(" ", " "," ", "1950 - 2019 climate" = 3, " " , " "," "," ")) %>%
  column_spec(1, width = "1cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "3cm") %>%
  #column_spec(6, width = ".5cm") %>%
  column_spec(7, width = "1.4cm") %>%
  column_spec(8, width = "1cm") %>%
  #column_spec(9, width = "2cm") %>%
  column_spec(10, width = "3cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
